PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-13 paper/ms.tex
paper: update tables with new modelcomp results
paper: cleanup tex
paper: update text per new modelcomp results

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
% \submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

%\objectname{PTFO 8-8695}
%\objectname{PTFO 8-8695b}
%\objectname{CVSO 30}

@@

%\title{Against the Planetary Interpretation of PTFO$\,$8-8695b}
% \title{Seeing Double: Still Against the Planetary Interpretation of
% PTFO$\,$8-8695b}
% \title{Seeing Double: TESS and Gaia Show That PTFO$\,$8-8695b is Unlikely a
% Planet}
%\title{Seeing Double: Indications From {\it TESS} and {\it Gaia} That
%PTFO$\,$8-8695b is Not a Planet}
%\title{Double Trouble: Transient Dips and Photometric Binarity in
%PTFO$\,$8-8695}
% \title{Double, Double, Spin plus Nubble: Two Stars and Two Signals in
% PTFO 8-8695}
% \title{PTFO\,8-8695: A binary star, not a hot Jupiter host}   
%\title{Two Stars and Two Signals in PTFO 8-8695}
\title{PTFO 8-8695: Two Stars, Two Signals, No Planet}

@@

% PENDING yy
\author[0000-0002-2457-272X]{D.~R.~Louie} % danalouie@astro.umd.edu
\affiliation{Department of Astronomy, University of Maryland, College
Park, MD 20742, USA}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \ptfo\ (Sector 6, Orbit 19).} {\it Top}:
    The original (\texttt{PDCSAP} mean-subtracted) relative flux.
    The beat period of 4.48 days is visible by eye.  The blue curve is
    a model including 2 harmonics at the longer period $P_{\rm \ell}$,
    plus 2 harmonics and a transit at the shorter period $P_{\rm s}$.
    {\it Upper middle}: Longer-period signal, equal to the original signal
    minus the shorter-period signal.  {\it Lower middle}:
    Shorter-period signal, equal to the original signal minus the
    longer-period signal.  {\it Bottom}: residual relative flux.  The
    data are binned from 2 to 10 minute cadence as a convenience for
    plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

@@

With the Gaia astrometry, it has become clear that 25$\,$Ori itself
has distinct subgroups
\citep{kounkel_apogee2_2018,briceno_cidaII_2019}.  In describing the
cluster membership of \ptfo, we follow the notation and results of
\citet{kounkel_apogee2_2018}.  These authors combined astrometric data
from Gaia DR2 with near-infrared spectra from APOGEE-2
\citep{gunn_sdss_2006,majewski_apache_2017,blanton_sloan_2017,zasowski_target_2017,cottle_apogee2_2018}.
They performed a hierarchical clustering on the six-dimensional
position and velocity information to identify subgroups within the
Orion complex.  From smallest to largest, \ptfo\ was identified as a
member of the following hierarchical subgroups:
\begin{equation}
  %{\rm PTFO\,8\text{-}8695}
  % \in
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where `$\subset$' means ``is a proper subset of''.  25$\,$Ori-1 is the
largest subgroup of 25$\,$Ori, with 149 identified members.  Based on
the color-magnitude diagram (CMD), the mean age was found to be
6.9$\,$Myr, while the HR diagram led to an estimated age of 8.5$\,$Myr
\citep[see][Section 2.3]{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} identified seven other smaller groups in
the Orion complex near the Be star 25$\,$Ori. These groups received
higher numbers, {\it e.g.}, 25$\,$Ori-2 (${\rm Age}_{\rm CMD}
=15.1\,$Myr; ${\rm Age}_{\rm CMD} =12.9\,$Myr; see also
\citealt{briceno_cidaII_2019}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.93\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Relative flux at the longer period, as in
    Figure~\ref{fig:splitsignal}.  {\it Bottom}: Relative flux at the
    shorter period. The reference phase is set to the dip.  Gray
    points are the 10 minute cadence \texttt{PDCSAP} flux.  Black
    points are binned to 100 points per period.
    The model (blue line)
    includes 2 harmonics at the longer period,
    plus 2 harmonics and a transit at the shorter period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

As an example, one possible model consists of a transit, $N_{\rm s}=2$
sines and cosines at the shorter period, plus $N_{\rm \ell}=1$ sine
and cosine at the longer period.  In this case, the free parameters
would be as follows.  The transit model parameters are the impact
parameter, the planet-to-star radius ratio, two quadratic limb
darkening parameters, the planet's orbital period (set equal to
$P_{\rm s}$) the time of a particular transit, and the mean flux.
There would be $2N_{\rm s}=4$ additional Fourier amplitudes at the
shorter period, plus $2N_{\rm \ell}=2$ Fourier amplitudes at the
longer period, as well as $P_\ell$ itself and the relative phase
$\phi_\ell$.  The total number of parameters is 14.

@@

We considered nine models, with the number of modes per frequency
$N_{\rm s}$ and $N_{\rm \ell}$ ranging from one to three.  To select
our preferred model, we used the Bayesian information criterion
(Table~1).  The model with the lowest BIC had two modes at the shorter
10.76$\,$hr period, and two modes at the longer 11.98$\,$hr period.
Two other models had BIC values that provided comparable evidence
\citep{burnham_multimodel_2016}: one with ($N_{\rm s}=3$, $N_{\rm
\ell}=3$), and the other with ($N_{\rm s}=3$, $N_{\rm \ell}=2$).
All nine models have
reduced $\chi^2$ values ranging between 1.25 and 1.68, which suggests
a plausible though imperfect agreement between the data and the model
to within the formal uncertainties.  Table~2 gives the best-fitting
parameters for the preferred model, which has the lowest BIC value.

@@

In every model, the $11.98\,{\rm hr}$ variability is a simple sinusoid
with peak-to-peak amplitude $\approx$10\%.  The $10.76\,{\rm hr}$
variability is always more complex.  The overall impression is of a
distorted sinusoidal function, with a peak-to-peak amplitude of about
4\%.  The asymmetric sinusoid rises to a maximum near phase 0.25, and
reaches minimum brightness between phases $-0.5$ and $-0.25$.  Between
phases $-0.5$ and $0.0$ there appears to be complex shorter-timescale
variability, including an abrupt jump at phase $\approx -0.33$, and
ending with a ``dip'' of depth $\approx$1.2\%, lasting $\approx$0.75
hours.  The fact that the higher-order models lead to roughly
comparable BIC values suggests that these sharper features may indeed
be real, but that there is only weak statistical support for their
existence.

@@

Visually, the out-of-dip modulation at the 10.76$\,$hr period
resembles a slightly asymmetric sinusoid (Figure~\ref{fig:phasefold}).
Non-zero contributions in both the first and second harmonics are
detected (Table~2).  The first sine and cosine harmonic both have
amplitudes of roughly $0.9\pm0.1\%$.  The second sine harmonic has
amplitude $0.16 \pm 0.07\%$, so is non-zero at a significance of only
2.3$\sigma$.  The second cosine harmonic has negative amplitude $0.53
\pm 0.06\%$.  In our sign convention, the fact that it is negative
means that this component peaks at phase 0.25 and 0.75.

@@

The planetary interpretation however does not readily explain the
first sine and cosine harmonics.  Interpreting the sine component as
Doppler beaming would imply a secondary mass greater than the primary
($0.86\,M_\odot$).  Interpreting the cosine component as reflected or
emitted light from the planet's surface is nonsensical because the
sign is wrong---the planet would need to be {\it absorbing} light.

@@

The combination of TESS and Gaia data has clarified a few things about
the \ptfo\ system.  Our main results are as follows.
\begin{itemize}
  \item {\it The TESS light curve shows two periodic signals.} The
    ``long'' signal is a 10\% peak-to-peak sinusoid that repeats every
    11.98 hours.  The ``short'' signal is a 4\% peak-to-peak ``dip +
    asymmetric sinusoid'' that repeats every 10.76 hours. The signals
    beat, and therefore cannot be an artifact linked to data
    processing.  Within the angular resolution of the Gaia source
    catalog, both signals need to originate from \ptfo.
  \item {\it The Gaia data imply binarity.} Relative to stars in its
    kinematic group, \ptfo\ is a photometric binary
    (Figure~\ref{fig:gaia}, top).  Relative to stars in its group that
    are at least as photometrically variable, \ptfo\ also shows signs
    of astrometric binarity (Figure~\ref{fig:gaia}, bottom).
  \item {\it The orbital phase of the dip has changed since the
    discovery by \citet{van_eyken_ptf_2012}.} As shown in
    Figure~\ref{fig:o_minus_c}, the phase seems to have jumped,
    perhaps twice. This agrees with the recent study by
    \citet{tanimoto_evidence_2020}.
  \item {\it All properties of \ptfo\ are consistent with the emerging
    class of transient and persistent flux dip stars.} Analogous
    light curves are shown in Figure~\ref{fig:brethren}.  Properties of
    this variability class are enumerated in
    Section~\ref{subsec:dipstars}.
\end{itemize}

The physical mechanism that explains the transient and persistent flux
dips is unresolved. Our preferred explanations include transiting
clumps of gas at the Keplerian corotation radius, and occultations of
starspots by an optically thick disk \citep[{\it
e.g.},][]{stauffer_orbiting_2017,david_transient_2017,zhan_complex_2019}.
The jumping orbital phase disfavors the explanation of an enshrouded,
transiting protoplanet.  Though \ptfob\ may not be a planet, as we and
others had hoped, understanding \ptfo\ and its analogs is a worthy
problem that might even teach us about the natal environments of the
majority of habitable-zone Earth-sized planets in the Milky Way
\citep{dressing_occurrence_2013}.

@@

\acknowledgements
When this manuscript was at an advanced stage, we learned of the
complementary work by \citet{koen_2020}, which was in press at the
{\it Monthly Notices} before submission of our manuscript.  Our
studies independently reached the key conclusions that the TESS
light curve shows two periodic signals, and that the properties of
\ptfo\ are consistent with the emerging class of transient and
persistent flux dip stars.  \citet{koen_2020} reached these
conclusions by modeling the TESS light curve as a truncated sum of
Fourier terms, and concluded that the two signals are most simply
interpreted as coming from two stars.  Our analysis of the Gaia data
provide independent support for the conclusion that \ptfo\ is a
binary.

Minor differences in our approaches are that \citet{koen_2020}
interprets the ``out of dip'' signal to potentially show multiple
dips, while our BIC-based model comparison did not indicate that
including additional harmonics past the second order was strictly
necessary (Table~1). Our analysis emphasized the agreement between the
TESS dip ephemeris and that from \citet{tanimoto_evidence_2020}.
\citet{koen_2020} however made a clearer case for testing the binarity
hypothesis using interferometric imaging and high-precision radial
velocities.
\\
\\
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank D.~Fabrycky, S.~Mahadevan, G.~Stef\'ansson, and
A.~Vanderburg for helpful calculations, observations, and suggestions.
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
\ptfo\ was included on the TESS ``short-cadence'' target list thanks
to the Guest Investigator programs of S.\ Czesla and C.\ Huang
(G011128 and G011132 respectively).
%
Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center for the production of the SPOC data products.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@

%
% The following are entries from Table 1 that are not otherwise cited
% in the text
%
% \nocite{wilson_wasp-4b_2008}
% \nocite{gillon_improved_2009}
% \nocite{winn_transit_2009}
% \nocite{hoyer_tramos_2013}
% \nocite{dragomir_terms_2011}
% \nocite{sanchis-ojeda_starspots_2011}
% \nocite{nikolov_wasp-4b_2012}
% \nocite{ranjan_atmospheric_2014}
% \nocite{huitson_gemini_2017}

% \input{WASP-4b_transit_time_table.tex}
% \input{WASP-4b_rv_table.tex}
% \input{model_fit_table.tex}
% \input{rv_model_posterior_table.tex}
% \input{pdot_table.tex}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{Two Stars, Two Signals, No Planet}

@@

% \title{Double, Double, Spin plus Nubble: Two Stars and Two Signals in
% PTFO 8-8695}
\title{PTFO 8-8695: Two Stars, Two Signals, No Planet}

@@

%CONFIRMED
\author[0000-0002-2457-272X]{D.~R.~Louie} % danalouie@astro.umd.edu
\affiliation{Department of Astronomy, University of Maryland, College
Park, MD 20742, USA}

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \ptfo\ (Sector 6, Orbit 19).} {\it Top}:
    The original (\texttt{PDCSAP} mean-subtracted) relative flux.
    The beat period of 4.48 days is visible by eye.  The blue curve is
    a model including 2 harmonics at the longer period $P_{\rm \ell}$,
    plus 3 harmonics and a transit at the shorter period $P_{\rm s}$.
    {\it Upper middle}: Longer-period signal, equal to the original signal
    minus the shorter-period signal.  {\it Lower middle}:
    Shorter-period signal, equal to the original signal minus the
    longer-period signal.  {\it Bottom}: residual relative flux.  The
    data are binned from 2 to 10 minute cadence as a convenience for
    plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

@@

With the Gaia astrometry, it has become clear that 25$\,$Ori itself
has distinct subgroups
\citep{kounkel_apogee2_2018,briceno_cidaII_2019}.  In describing the
cluster membership of \ptfo, we follow the notation and results of
\citet{kounkel_apogee2_2018}.  These authors combined astrometric data
from Gaia DR2 with near-infrared spectra from APOGEE-2
\citep{gunn_sdss_2006,majewski_apache_2017,blanton_sloan_2017,zasowski_target_2017,cottle_apogee2_2018}.
They performed a hierarchical clustering on the six-dimensional
position and velocity information to identify subgroups within the
Orion complex.  From smallest to largest, \ptfo\ was identified as a
member of the following hierarchical subgroups:
\begin{equation}
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where `$\subset$' means ``is a proper subset of''.  25$\,$Ori-1 is the
largest subgroup of 25$\,$Ori, with 149 identified members.  Based on
the color-magnitude diagram (CMD), the mean age was found to be
6.9$\,$Myr, while the HR diagram led to an estimated age of 8.5$\,$Myr
\citep[see][Section 2.3]{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} identified seven other smaller groups in
the Orion complex near the Be star 25$\,$Ori. These groups received
higher numbers, {\it e.g.}, 25$\,$Ori-2 (${\rm Age}_{\rm CMD}
=15.1\,$Myr; ${\rm Age}_{\rm CMD} =12.9\,$Myr; see also
\citealt{briceno_cidaII_2019}).

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Relative flux at the longer period, as in
    Figure~\ref{fig:splitsignal}.  {\it Bottom}: Relative flux at the
    shorter period. The reference phase is set to the dip.  Gray
    points are the 10 minute cadence \texttt{PDCSAP} flux.  Black
    points are binned to 100 points per period.
    The model (blue line)
    includes 2 harmonics at the longer period,
    plus 3 harmonics and a transit at the shorter period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

As an example, one possible model consists of a transit, $N_{\rm s}=2$
sines and cosines at the shorter period, plus $N_{\rm \ell}=1$ sine
and cosine at the longer period.  In this case, the free parameters
would be as follows.  The transit model parameters are the impact
parameter, the planet-to-star radius ratio, two quadratic limb
darkening parameters, the planet's orbital period (set equal to
$P_{\rm s}$) the time of a particular transit, and the mean flux.  We
also independently sampled the stellar radius and mass, implicitly
defining the stellar density.  Additionally, there would be $2N_{\rm
s}=4$ additional Fourier amplitudes at the shorter period, plus
$2N_{\rm \ell}=2$ Fourier amplitudes at the longer period, as well as
$P_\ell$ itself and the relative phase $\phi_\ell$.  The total number
of parameters would be 17.

@@

We considered nine models, with the number of modes per frequency
$N_{\rm s}$ and $N_{\rm \ell}$ ranging from one to three.  To select
our preferred model, we used the Bayesian information criterion
(Table~1).  The model with the lowest BIC had three modes at the
shorter 10.76$\,$hr period, and two modes at the longer 11.98$\,$hr
period.
The other models had BIC values that implied significantly less
support \citep{burnham_multimodel_2016}.
All nine models have
reduced $\chi^2$ values ranging between 1.21 and 1.68, which suggests
a plausible though imperfect agreement between the data and the model
to within the formal uncertainties.  Table~2 gives the best-fitting
parameters for the preferred model, which has the lowest BIC value.

@@

In every model, the $11.98\,{\rm hr}$ variability is a simple sinusoid
with peak-to-peak amplitude $\approx$10\%.  The $10.76\,{\rm hr}$
variability is always more complex.  The overall impression is of a
distorted sinusoidal function, with a peak-to-peak amplitude of about
4\%.  The asymmetric sinusoid rises to a maximum near phase 0.25, and
reaches minimum brightness between phases $-0.5$ and $-0.25$.  Between
phases $-0.5$ and $0.0$ there appears to be complex shorter-timescale
variability, ending with a ``dip'' of depth $\approx$1.2\%, lasting
$\approx$0.75 hours.  The fact that our preferred model has three
rather than two ``short period'' harmonics is linked to the degree of
curvature required between phases $-0.5$ and $-0.05$: the analogous
$(N_{\rm \ell},N_{\rm s})=(2,2)$ model prefers a longer transit duration,
but does not fit the out-of-transit curvature as well, particularly
immediately before ingress.

@@

Visually, the out-of-dip modulation at the 10.76$\,$hr period
resembles a slightly asymmetric sinusoid (Figure~\ref{fig:phasefold}).
Non-zero contributions in both the first and second harmonics are
detected (Table~2).  The first sine and cosine harmonic both have
amplitudes of roughly $0.90\pm0.04\%$.  The second sine harmonic has
amplitude $0.16 \pm 0.04\%$, so is non-zero at a significance of
$\approx$4$\sigma$.  The second cosine harmonic has negative amplitude $0.55
\pm 0.03\%$.  In our sign convention, the fact that it is negative
means that this component peaks at phase 0.25 and 0.75.

@@

The planetary interpretation however does not readily explain the
large first sine and cosine harmonics.  Interpreting the sine component as
Doppler beaming would imply a secondary mass greater than the primary
($0.86\,M_\odot$).  Interpreting the cosine component as reflected or
emitted light from the planet's surface is nonsensical because the
sign is wrong---the planet would need to be {\it absorbing} light.

@@

The combination of TESS and Gaia data has clarified a few things about
the \ptfo\ system.  Our main results are as follows.
\begin{itemize}
  \item {\it The TESS light curve shows two periodic signals.} The
    ``long'' signal is a 10\% peak-to-peak sinusoid that repeats every
    11.98 hours.  The ``short'' signal is a 4\% peak-to-peak ``dip +
    asymmetric sinusoid'' that repeats every 10.76 hours. The signals
    beat, and therefore cannot be an artifact linked to data
    processing.  Within the angular resolution of the Gaia source
    catalog, both signals originate from \ptfo.
  \item {\it The Gaia data imply binarity.} Relative to stars in its
    kinematic group, \ptfo\ is a photometric binary
    (Figure~\ref{fig:gaia}, top).  Relative to stars in its group that
    are at least as photometrically variable, \ptfo\ also shows signs
    of astrometric binarity (Figure~\ref{fig:gaia}, bottom).
  \item {\it The orbital phase of the dip has changed since the
    discovery by \citet{van_eyken_ptf_2012}.} As shown in
    Figure~\ref{fig:o_minus_c}, the phase seems to have jumped,
    perhaps twice. This agrees with the recent study by
    \citet{tanimoto_evidence_2020}.
  \item {\it All properties of \ptfo\ are consistent with the emerging
    class of transient and persistent flux dip stars.} Analogous
    light curves are shown in Figure~\ref{fig:brethren}.  Properties of
    this variability class are enumerated in
    Section~\ref{subsec:dipstars}.
\end{itemize}

The physical mechanism that explains the transient and persistent flux
dips is unresolved. Our preferred explanations include transiting
clumps of gas at the Keplerian corotation radius, and occultations of
starspots by a tenuous gas disk \citep[{\it
e.g.},][]{stauffer_orbiting_2017,david_transient_2017,zhan_complex_2019}.
The jumping orbital phase disfavors the explanation of an enshrouded,
transiting protoplanet.  Though \ptfob\ may not be a planet, as we and
others had hoped, understanding \ptfo\ and its analogs is a worthy
problem.  It might even teach us about the birth environments of the
majority of habitable-zone Earth-sized planets
\citep{dressing_occurrence_2013}.

@@

\acknowledgements
When this manuscript was at an advanced stage, we learned of the
complementary work by \citet{koen_2020}, which was in press at the
{\it Monthly Notices} before submission of our manuscript.  Our
studies independently reached the key conclusions that the TESS
light curve shows two periodic signals, and that the properties of
\ptfo\ are consistent with the emerging class of transient and
persistent flux dip stars.  \citet{koen_2020} reached these
conclusions by modeling the TESS light curve as a truncated sum of
Fourier terms, and concluded that the two signals are most simply
interpreted as coming from two stars.  Our analysis of the Gaia data
provide independent support for the conclusion that \ptfo\ is a
binary, and emphasized the agreement between the
TESS dip ephemeris and that from \citet{tanimoto_evidence_2020}.
\\
\\
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%
The authors thank D.~Fabrycky, S.~Mahadevan, G.~Stef\'ansson, and
A.~Vanderburg for helpful calculations, observations, and suggestions.
%
We also thank the Heising-Simons Foundation for
their generous support of this work.
%
\ptfo\ was included on the TESS ``short-cadence'' target list thanks
to the Guest Investigator programs of S.\ Czesla and C.\ Huang
(G011128 and G011132 respectively).
%
Resources supporting this work were provided by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center for the production of the SPOC data products.
%
The Digitized Sky Survey was produced at the Space Telescope Science
Institute under U.S. Government grant NAG W-2166.
Figure~\ref{fig:scene} is based on photographic data obtained using
the Oschin Schmidt Telescope on Palomar Mountain.
%
% %
% Based on observations obtained at the Gemini Observatory, which is
% operated by the Association of Universities for Research in Astronomy,
% Inc., under a cooperative agreement with the NSF on behalf of the
% Gemini partnership: the National Science Foundation (United States),
% National Research Council (Canada), CONICYT (Chile), Ministerio de
% Ciencia, Tecnolog\'{i}a e Innovaci\'{o}n Productiva (Argentina),
% Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e Inova\c{c}\~{a}o (Brazil),
% and Korea Astronomy and Space Science Institute (Republic of Korea).
% %
% Observations in the paper made use of the High-Resolution Imaging
% instrument Zorro at Gemini-South. Zorro was funded by the NASA
% Exoplanet Exploration Program and built at the NASA Ames Research
% Center by Steve B. Howell, Nic Scott, Elliott P. Horch, and Emmett
% Quigley.
% %
% This research has made use of the VizieR catalogue access tool, CDS,
% Strasbourg, France. The original description of the VizieR service was
% published in A\&AS 143, 23.
% %
% This work has made use of data from the European Space Agency (ESA)
% mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
% by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
% \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
% for the DPAC has been provided by national institutions, in particular
% the institutions participating in the {\it Gaia} Multilateral
% Agreement.
%
% (Some of) The data presented herein were obtained at the W. M. Keck
% Observatory, which is operated as a scientific partnership among the
% California Institute of Technology, the University of California and
% the National Aeronautics and Space Administration. The Observatory was
% made possible by the generous financial support of the W. M. Keck
% Foundation.
% The authors wish to recognize and acknowledge the very significant
% cultural role and reverence that the summit of Maunakea has always had
% within the indigenous Hawaiian community.  We are most fortunate to
% have the opportunity to conduct observations from this mountain.
%
% \newline
%

@@
